Online {\IterComp}

### 2017-11-14 motivation.tex
adds fall-back results of I.C. with IPC and 1/Runtime
adds text about offline I.C. with IPC in motivation

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose. To show this, we ran
    each of the \FIXME{32} \textit{KDataSets} benchmarks 1,000 times, each time with a different input \textit{and} a different optimized
    binary, and we measured three metrics: runtime, inverse runtime, and IPC. \FIXME{Fig.XXX} shows the correlation coefficient between
    them and a reasonable efficiency metric, speedup over \texttt{-O0}. For all benchmarks, the correlation coefficient is below
    \FIXME{0.20} for runtime and below \FIXME{0.35} for inverse runtime. Both have obvious reasons for being inappropriate efficiency
    metrics. Doubling the amount of data to be processed will cause the runtime to rise and the inverse runtime to fall, even if we use the same binary.
    Efficiency has nothing to do with it. IPC also correlates poorly with efficiency, the correlation coefficient being just \FIXME{0.15}.
    While it is used often in computer architecture, it works there because it is used with invariant binaries. In contrast, any compiler
    optimization that trades high latency instructions for multiple low latency instructions can reduce IPC while improving efficiency.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/corr_coeff.pdf}
    \caption{Correlation coefficient.}
    \label{fig:corr_coeff}
\end{figure*}

>>>>

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose.
    \FIXME{Evidence1:}
    To show this, we performed iterative compilation guided by IPC for the same set of 10 inputs
    discussed in Figure~\ref{fig:motivation_wrong_inputs} and compare with the previous approach which optimizes directly for execution time.
    The best optimization sequence found in Figure~\ref{fig:motivation_wrong_inputs}
    has an average speedup of 1.7 over \texttt{-O3} and an average IPC of 2.59.
    However, iterative compilation guided by IPC is able to find an optimization
    sequence that produces a higher IPC of 2.72 but an average slowdown of 0.98.
    This result agrees with the known fact that higher IPC does not necessarily translate to lower execution time when comparing different versions of the program.
    \FIXME{Evidence2:}
    To show this, we ran
    each of the \FIXME{32} \textit{KDataSets} benchmarks 1,000 times, each time with a different input \textit{and} a different optimized
    binary, and we measured three metrics: runtime, inverse runtime, and IPC. \FIXME{Fig.XXX} shows the correlation coefficient between
    them and a reasonable efficiency metric, speedup over \texttt{-O0}. For all benchmarks, the correlation coefficient is below
    \FIXME{0.20} for runtime and below \FIXME{0.35} for inverse runtime. Both have obvious reasons for being inappropriate efficiency
    metrics. Doubling the amount of data to be processed will cause the runtime to rise and the inverse runtime to fall, even if we use the same binary.
    Efficiency has nothing to do with it. IPC also correlates poorly with efficiency, the correlation coefficient being just \FIXME{0.15}.
    While it is used often in computer architecture, it works there because it is used with invariant binaries. In contrast, any compiler
    optimization that trades high latency instructions for multiple low latency instructions can reduce IPC while improving efficiency.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/motivation-speedups.pdf}
    \caption{\FIXME{[Fall-back Result]} Performance improvement of iterative compilation guided by IPC and runtime.}
    \label{fig:motivation-speedups}
\end{figure*}
